---
title: " "
format:
  pdf:
    toc: false
    page-layout: full
    margin-right: 1in
    margin-left: 1in
    margin-top: 1.15in
    margin-bottom: 1.25in
    include-in-header:
      text: |
        \usepackage{fontawesome5}
        \usepackage{academicons}
engine: knitr
editor: 
  markdown: 
    wrap: 72
---

\begin{center}
\Large\textbf{Margherita Calderan, Ph.D.}

\normalsize\text{My research interests include computational models of cognition, Bayesian statistics, and metascience.}

\faEnvelope\ \href{mailto:margherita.calderan@gmail.com}{margherita.calderan@gmail.com}\\[0.2em]
\faGithub\ \href{https://github.com/Mar-Cald}{github.com/Mar-Cald} \quad
\aiOverleaf\ \href{https://gitlab.pavlovia.org/mar.cald}{gitlab.pavlovia.org/mar.cald} \quad
\aiResearchGate\ \href{https://www.researchgate.net/profile/Margherita-Calderan-2}{ResearchGate} \quad
\aiOSF\ \href{https://osf.io/profile/}{OSF}
\end{center}

```{r}
#| label: cvevents
#| echo: false

cvevents <- function(tbl, when, what, where, details = NULL) {
  result <- ""
  for (i in seq_len(nrow(tbl))) {
    header <- paste0("**", tbl[[what]][i], "**  \n")
    institution <- paste0("_", tbl[[where]][i], "_  \n")
    date <- paste0(tbl[[when]][i], "\n")  # Single \n instead of "  \n"
    
    block <- paste0(header, institution, date)

    if (!is.null(details)) {
      detail_items <- tbl[[details]][[i]]
      if (length(detail_items) > 0) {
        # Keep one \n for Markdown list formatting
        block <- paste0(block, "\n")
        for (item in detail_items) {
          block <- paste0(block, "  - ", item, "\n")
        }
      }
    }
    block <- paste0(block, "\n")
    result <- paste0(result, block)
  }
  knitr::asis_output(result)
}


```

------------------------------------------------------------------------

## Current Position

```{r}
#| label: experience
#| output: asis
#| echo: false
tibble::tribble(
    ~role, ~institution, ~dates, ~details, ~tasks,
    "Postdoctoral Researcher", "Department of General Psychology, University of Padova, Italy", "Oct. 2024 - Present",
    " ", c("Tails or types? Testing the dimensional hypothesis in neurodevelopmental disorders", "Supervisor: Prof. Enrico Toffalini",
           "1.5 year research grant")) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```


## Education

```{r }
#| label: education
#| output: asis
#| echo: false
tibble::tribble(
    ~degree, ~institution, ~dates, ~details,
    "Ph.D. in Psychological Sciences - cum laude", "University of Padova, Italy", "Oct. 2021 - Oct. 2024", 
      c("Thesis: Balancing stability and flexibility in cognitive control and learning: the effects of arousal", 
        "Supervisors: Prof. Roberta Sellaro, Prof. Nicola Cellini"),
     "Postgraduate Internship", "Psychophysiology Lab, University of Padova, Italy", "Jan. 2021 - Dec. 2021", c(
        "Investigated the role of sleep characteristics in false memory formation and emotional reactivity.",
        "Supervisors: Prof. Andrea Spoto, Prof. Nicola Cellini"),
    "M.Sc. in Cognitive Neuroscience and Clinical Neuropsychology - 110 cum laude", "University of Padova, Italy", "Oct. 2018 - Dec. 2020", 
      c("Thesis: Sleep characteristics in adults with high functioning autism: a polysomnographic study", "Supervisor: Prof. Nicola Cellini"),
    "Curricular Internship", "Psychophysiology Lab, University of Padova, Italy", "Dec. 2019 - Aug. 2020", c(
        "Analyzed polysomnographic data to examine sleep architecture in young adults with high-functioning autism.",
        "Collaborated with the University of Trento and the University of Tübingen.",
        "Supervisor: Prof. Nicola Cellini"
    ),
    "B.S. in Cognitive Psychology and Psychobiology - 109/110", "University of Padova, Italy", "Sept. 2015 - July 2018", 
      c("Thesis: Gender differences in the long-term consolidation of emotional memories", 
        "Supervisor: Prof. Michela Sarlo")
) |>
  cvevents(when = "dates", what = "degree", where = "institution", details = "details")
```

\newpage

## Abroad

```{r}
#| label: Abroad 
#| output: asis
#| echo: false
tibble::tribble(
    ~role, ~institution, ~dates, ~details, ~tasks,
    "Visiting PostDoc", "Department of Biomedical Data Sciences, Leiden University Medical Center, the Netherlands", "1.5 months (Sept. 2025 - Oct. 2025)",
    "", c(
        "Research on Bayesian approaches to the problem of multiplicity.",
        "Supervisor: Prof. Jelle Goeman"
    ),
    "Visiting PhD student", "Cognitive Psychology Unit, University of Leiden, the Netherlands", "4 months (Feb. 2024 - Jun. 2024)",
    "", c(
        "Research about the effects of mind-wandering on cognitive flexibility.",
        "Supervisor: Prof. Bryant Jongkees"
    ),
         "Research Intern", "Donders Sleep and Memory Lab, Donders Institute, the Netherlands", "2 months (Jun. 2019 – Aug. 2019)",
    "", c(
        "Assisted with a project on the association between affective memory bias, medial prefrontal schema processing, and sleep in depressed patients and healthy controls.",
        "Assisted with a project on lucid dream induction.",
        "Supervisor: Prof. Martin Dresler"
    ),
    "Erasmus +", "Jaume I University, Spain", "5 months (Feb. 2015 – July. 2015)",
    " ", c("Completed a semester-long academic exchange as part of my undergraduate studies.")
    ) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```

\newpage

## Publications

### In Press

1. **Calderan, M.**, Visalli, A., Degasperi, G., Toffoli, L., Sellaro,
    R., & Cellini, N. Predictions under sleep restriction: The effects
    of partial sleep deprivation on learning and inhibitory control.
    Accepted for publication in *Royal Society Open Science*, <https://doi.org/10.1098/rsos.252345>. **Preprint:** <https://doi.org/10.31234/osf.io/x7m4z\_v3>.

### Published

1.  **Calderan, M.**, Jongkees, J.B., Gambarota, F., Pastore, M.,
    Cellini, N., & Sellaro, R. (2025) Isolating working memory gating processes
    under stress. *Collabra::Psychology*. <https://doi.org/10.1525/collabra.140750>; **OSF** repo: <https://osf.io/d43vs/> 

2.  **Calderan, M.**, Toffalini, E., Mirandola, C., & Cellini, N.
    (2025). Sleep does not affect false memory production on a
    script-based test. *Neuropsychologia*.
    <https://doi.org/10.1016/j.neuropsychologia.2025.109210>; **OSF** repo: <https://osf.io/kwycq/> 

3.  Toffoli, L., **Calderan, M.**, Del Popolo Cristaldi, F., Duma, G.
    M., Calcagnì, A., Pastore, M., Tarantino, V., & Mento, G. (2025).
    Can I afford one more candy? How motivational contexts shape
    adaptive cognitive control in children. *Developmental Psychology*.
    <https://doi.org/10.1037/dev0001976>; **OSF** repo: <https://osf.io/shuq2/> 

4.  Sobol, M., Błachnio, A., **Calderan, M.**, Degasperi, G., Mioni, G.,
    Hryhorchuk, I., Plucińska, E., Stasiniewicz, J., Kwapiński, J.,
    Jankowski, K., & Cellini, N. (2025). Balanced time perspective as a
    factor mitigating the negative consequences of sleep disruptions in
    the perinatal period. *Chronobiology International*, 1–12.
    <https://doi.org/10.1080/07420528.2025.2490499> 

5.  **Calderan, M.**, & Visalli, A. (2024). Challenges of meta-learning
    and rational analysis in large worlds. *Behavioral and Brain
    Sciences*, 47, e148.
    <https://doi.org/10.1017/S0140525X24000128>.


### Under Review

1.  Visalli, A., Calistroni, F. M., **Calderan, M.**, Donnarumma, F.,
    Zorzi, M., & Ambrosini, E. A computational framework for integrating
    Predictive processes with evidence Accumulation Models (PAM). Under
    Review in *Behavior Research Methods*. **Preprint:**
    <https://doi.org/10.48550/arXiv.2411.13203>.

2.  Toffalini, E., **Calderan, M.**, Pagan, R., Tobia, V. & Sonuga-Barke, E. A   Critical Tails or Types? A Critical Systematic Review of Taxometric Studies of  Neurodevelopmental Conditions. Under review in *JCPP Advances* <https://github.com/EnricoToffalini/Taxometrics-Neurodevelopmental-Disorders/tree/main>

3.  Mazzoni, N., Kurz, E.V., Cellini, N., Ciringione, L., **Calderan, M.**, Gallitto, G., Falco, S., Venuti, P., Zinke, K., Born, J., & Carìa, A., Aperiodic and periodic neural activity during sleep in autism spectrum disorders. Under Review in *BMC medicine*.

### Preregistration

1.  Sirota, M., Šrol, J., Lisi, M., Juanchich, M., Guglani, K.,
    Silverstein, P., … **Calderan, M.**, ... Schmidt, K. (2025, January
    14). Mapping and Increasing Error Correction Behaviour in a
    Culturally Diverse Sample. **Preprint:**
    <https://doi.org/10.17605/OSF.IO/WN4VX>.

2.  Toffalini, E., **Calderan, M.**, Feraco, T., & Gambarota, F. Link
    Functions and Generalized Linear Models in Interaction Testing
    within Psychological Research. <https://osf.io/sjdu4>

### In Preparation

1.  Barbiero, J., **Calderan, M.**, & Mioni, G., The contribution of
    cerebellum in time perception: A systematic review and
    meta-analyses. In preparation for *Wiley Interdisciplinary
    Reviews-Cognitive Science*

2.  Toffoli, L., **Calderan, M.**, Stefanelli, G., Duma, G.M., Del
    Popolo Cristaldi, F., Duma, G., Pastore, M., Frisina, S., Tarantino,
    V., & Mento, G., I am talking to you! Engagement modulates the
    effects of digital contents exposure on preschoolers’ adaptive
    cognitive control. In preparation for *Developmental Sciences*.

3.  **Calderan, M.**, van Dooren, R., Sellaro, R., & Jongkees, J.B.,
    Dynamic and contextual modulation of constraints on cognitive
    control. In preparation for *Journal of Experimental Psychology:
    Human Perception and Performance*.

### Published Abstract

1.  **Calderan, M.**, Visalli, A., Sellaro, R., & Cellini, N. (2024).
    Restless Sleep, Uncertain Minds: Learning and Inhibitory Control
    Under Partial Sleep Deprivation. Proceedings of the Annual Meeting
    of the Cognitive Science Society, 46.
    <https://escholarship.org/uc/item/65b2f0n7>.

2.  **Calderan, M.**, Visalli, A., Sellaro, R., & Cellini, N., (2024).
    The Effects of Partial Sleep Deprivation on Adaptive Cognitive
    Control. *Sleep Medicine*,
    <https://doi.org/10.1016/j.sleep.2023.11.156>.

3.  **Calderan, M.**, Visalli, A., Sellaro, R., & Cellini, N. (2024).
    Expecting the unexpected: a closer look at the effect of partial
    sleep deprivation on learning and inhibitory control. *Journal of
    Sleep Research*, <https://doi.org/10.1111/jsr.14291>.

4.  Baldassarri, A., Colombo, C., Bergamo, D., **Calderan, M.**,
    Varanini, A., Ferrentino, A.,D’atri, A., & Cellini, N. (2024).
    Exploring the impact of oscillatory events during a nap on emotional
    memory consolidation. *Journal of Sleep Research*,
    <https://doi.org/10.1111/jsr.14291>

\newpage

## Conferences

1.  Stefanelli G., Toffoli L., **Calderan M.**, Del Popolo Cristaldi F.,
    Duma G. M., Tarantino V., Visalli A., Sellaro R., Mento G.
    Apprendimento associativo implicito e volatilità ambientale
    nell’ADHD. **Video-Poster** at Giornate di aggiornamento sull’uso
    degli strumenti in Psicologia Clinica dello Sviluppo Bologna
    (Italy), February 2025.

2.  Stefanelli G., Toffoli L., **Calderan M.**, Duma G. M., Del Popolo
    Cristaldi F., Tarantino V., Visalli A., Sellaro R. & Mento G. Super
    Learning Bros: Developmental trajectories of probabilistic learning
    in volatile environment. **Talk** at the Cognitive Science Arena,
    Brixen (Italy), February 2025.

3.  **Calderan, M.**, Visalli, A., Degasperi, G., Calistroni, F.M.,
    Sellaro, R., & Cellini, N. Expecting the unexpected: a closer look
    at the eﬀect of partial sleep deprivation on learning and inhibitory
    control. **Poster** presented at Sleep Europe 2024, Seville (Spain),
    September 2024.

4.  **Calderan, M.**, Visalli, A., Degasperi, G., Calistroni, F.M.,
    Sellaro, R., & Cellini, N. Restless Sleep, Uncertain Minds: Learning
    and Inhibitory Control Under Partial Sleep Deprivation. **Poster**
    presented at CogSci 2024: Dynamics of Cognition, Rotterdam
    (Netherlands), July 2024.

5.  Degasperi, G.,**Calderan, M.**, Mioni, G., Meisner, M., Blachnio,
    A., Hryhorchuk, I., Plucinska, E., Sobol, M., & Cellini, N. The role
    of sleep, circadian rhythms, balanced time perspective on perinatal
    depression symptoms. **Poster** at the Cognitive Science Arena,
    Brixen (Italy), February 2024.

6.  Toffoli, L.,**Calderan, M.**, Duma, G. M., Frisina, S., Tarantino
    V., & Mento, G. I'm talking to you! Interactive digital content
    effects on children's adaptive cognitive control. **Talk** at the
    Cognitive Science Arena, Brixen (Italy), February 2024.

7.  **Calderan, M.**, Visalli, A., Sellaro, R., & Cellini, N. The
    Effects of Partial Sleep Deprivation on Adaptive Cognitive Control.
    **Poster** presented at World Sleep Congress, Rio de Janeiro
    (Brasil), October 2023.

8.  **Calderan, M.**, Visalli, A., Sellaro, R., & Cellini, N. The
    sleep-deprived predictive brain: modeling the eﬀect of partial sleep
    deprivation on adaptive cognitive control. **Talk** at the XXIX
    Conference of the Italian Association of Psychology (AIP) -
    Experimental Psychology Section. Lucca (Italy), September 2023.

9.  **Calderan, M.**, Cellini, N., Sellaro, R., Stressed Minds:
    Unraveling Acute-Stress Effects on Working Memory Processes.
    **Mini-Talk** at the Cognitive Science Arena, Brixen (Italy),
    February 2023.

10. Toffoli, L., **Calderan, M.**, Del Popolo Cristaldi, F., Duma, G.
    M., Calcagnì, A., Pastore, M., Tarantino, V., & Mento, G. Can I
    afford one more candy? How motivational contexts shape adaptive
    cognitive control in children. **Talk** at the Cognitive Science
    Arena, Brixen (Italy), February 2023.

11. **Calderan, M.**, Cellini, N., Sellaro, R., Exploring the Influence
    of Stress on Working Memory Gating Mechanisms. **Mini-Talk** at the
    XXX Conference of the Italian Association of Psychology (AIP).
    Padova (Italy), September 2022.

12. **Calderan, M.**, Cellini, N., Sellaro, R., Understanding
    stress-induced Effects on Working Memory gating mechanisms.
    **Poster** presented at the 22nd meeting of the European Society for
    Cognitive Psychology (ESCoP), Lille (France), August 2022.

\newpage

## Invited talks

-  **Bayesian inference and multiple comparisons: From idealization of methods to conscious practice**. **C**ognitive **N**euroscience **S**eminars, Department of General Psychology,  University of Padova, Italy. 4th December 2025.

-   **From Cognitive Psychology to Bayesian Multiple Testing**. Medical Statistics Meeting, Department of Biomedical Data Sciences, Leiden University Medical Center, Leiden, The Netherlands. 23rd October 2025.

-   **Bayesian Multiple Testing**. STAT-Talk Series, Methodology and
    Statistics Department, Institute of Psychology, Leiden University,
    Leiden, The Netherlands. 18th September 2025.

## Awards and Grants

-   **Travel Grant**: European Conference on Visual Perception, Mainz (Germany).
-   **Travel Grant**: qHelp international seminar on Quantitative
    Psychology. Arrifana (Portugal)
-   **Painter Award**: Best Poster, Cognitive Science Arena, Brixen (Italy).
-   **Erasmus Placement Grant (2 Months)**: Donders Sleep and Memory
    Lab, Nijmegen (The Netherlands).
-   **Erasmus Placement Grant (5 Months)**: Jaume I University,
    Castellón de la Plana (Spain).

\newpage

## Peer Reviews

Ad-hoc reviewer (3 reviewed papers) for:

- Italian Journal of Applied Statistics (1)
- Frontiers in Psychology - Theoretical and Philosophical Psychology (1)
- Frontiers in Psychology - Cognition (1)

## Teaching

### Lectures on contract (docenze a contratto)

-   **Test per le organizzazioni** (21 hours, 3 CFU). 2nd semester of the 2025/2026 academic year. Lecturer (titolare di
    modulo) for the Master’s Degree in Psicologia Sociale, del Lavoro e
    della Comunicazione, University of Padova.

-   **Introduction to meta-analysis with application in R** (5 hours, 1
    CFU). Scheduled for the 2nd semester of the 2025/2026 academic year.
    Professor for the course within the PhD program in Psychological
    Sciences, University of Padova.

### Seminars

-   **Introduction to R**. An intensive R programming course offered
    within the ARCA (Applied Research Course Academy) courses,
    Department of Developmental Psychology and Socialization, University
    of Padova. Material: <https://github.com/arca-dpss/course-R-2425>
    -   December, 2024 (20 hrs.)
    -   April, 2025 (20 hrs.)
    -   November, 2025 (20 hrs.)
    -  May, 2026 (20 hrs., planned)
-   **Learning in Dynamic Environments: A Tentative Implementation of
    the Volatile Kalman Filter in STAN.** Presentation (1 hr.) on a
    Bayesian-based implementation of a learning algorithm for the
    2023/24 Psicostat meeting series:
    <https://psicostat.dpss.psy.unipd.it/meetings/slides/2024-03-22_calderan.pdf>

### Integrative teaching (Didattica integrativa)

-   **Assistance** during lectures for the course **Testing
    Psicologico** (Prof. Tatiana Marci), Bachelor's degree in Scienze psicologiche dello sviluppo, della personalità e delle relazioni interpersonali, University of Padova (14 hrs.). 

-   Preparation and correction of **practical group exercises** and
    exams for the course **Experimental Research Methods in Psychology**
    (Prof. Roberta Sellaro), Master's degree in Developmental and
    Educational Psychology, University of Padova (14 hrs.).

-   **Assistance** in the preparation of exercises and corrections for
    the course **General Psychology** (Prof. Enrico Toﬀalini),
    Bachelor's degree in Techniques and Methods in Psychological
    Sciences, University of Padova (15 hrs.).

-   **Assistance** during lectures and preparation of **practical group
    exercise** for the course **General Psychology** (Prof.Giovanna
    Mioni), Bachelor's degree in Social and Work Psychological Sciences,
    University of Padova (14 hrs.).

### Workshops

-   **The 3Rs of Trustworthy Science: Reproducibility, Replicability, and Robustness. Theory and Applications in R**. Pre-conference Workshop - **International Biometric Society**, Seul (South Korea). 12 July 2026. Planned hands-on methodological workshop held with Dr. Filippo Gambarota.

-   **Generalized Linear Models for Psychology: Understanding, Simulating, and Planning Your Analyses**. Pre-conference Workshop - **Cognitive Science Arena**, Brixen (Italy). 5 February 2026. Planned hands-on methodological workshop held with Dr. Filippo Gambarota.

-  **Bayesian Approaches To Multiplicity**. Psicostat HandZone on Bayesian Approaches To Multiplicity, Univeristy of Padova, Padova (Italy). 27 December 2025 (1.5 hr.). <https://psicostat.dpss.psy.unipd.it/pages/handzone.html>


-   **A Practical Introduction to Evidence Accumulation Models in Visual Perception Research**. Pre-conference Workshop - **European Conference on Visual Perception**, Mainz (Germany). 24 August 2025 (2.30 hr.). Hands-on methodological workshop held with Dr. Carolina Maria Oletto. Material: <https://mar-cald.github.io/eam-workshop/eam-home.html>.

-   **Introduction to Reproducible Science**. Pre-School workshop - **Replicability Crisis in Science**, Padova (Italy). 6 June 2025 (2
    hrs.). Material: <https://github.com/Mar-Cald/repro-pre-school>.

-   **Tempi di risposta**. Workshop on reaction time distributions,
    Univeristy of Padova, Padova (Italy). 10 June 2025 (1 hr.).
    Material: <https://mar-cald.github.io/tempi/>.

## Academic Roles

-  **Expert (Cultore della Materia) of Psychometrics (PSIC-01/C ex M-PSI/03)**
Department of Developmental Psychology and Socialization, University of Padova, Italy. January 2026-present.

-   **Representative of Research Fellows** in the Department of General
    Psychology, University of Padova. 02/2024 – Present

-   **Co-supervision of students** for their internships and
    Bachelor’s (2) and Master’s theses (1)

\newpage

## Organizational Activities

### Methodological School: Replicability Crisis in Science

Member of the **Organizing team**. The school aims to provide a broad
and interdisciplinary perspective on replicability, along with tools
that help participants explore aspects most relevant to their own field.
Lectures cover the epistemological, philosophical, and statistical
foundations of replicability and the so-called replication crisis.
Students engage in guided group activities to discuss core issues and
apply the course concepts to real data analysis. Padova (Italy).
(<https://psicostat.github.io/replicability-psy-unipd-phd>)

-   **Lecturers**: Prof. Branden Fitelson, Prof. Giovanni Parmigiani,
    Dr. Filippo Gambarota

### International Winter School - The 4 Ms: Meta-research, Measurement, Multi-lab, and Multiverse data analysis in Behavioral Sciences

Member of the **Organizing team**. The Winter School aims to address the
methodological challenges in behavioral sciences, which impact theory,
measurement, and data analysis. Its main purpose is to introduce
attendees to advancements in meta-research, providing both theoretical
insights and practical tools to conduct rigorous research. Additionally,
it aims to foster collaborative networks by enabling attendees to
discuss their ongoing projects with teachers and peers, facilitating new
collaborations and the application of the presented tools. Padova
(Italy). (<https://winterschool4ms.dpg.unipd.it/>)

-   **Lecturers**: Prof. Daniël Lakens, Prof. Dorothy Bishop, Prof.
    Jessica Flake, Prof. Lisa DeBruine, Prof. Ulrich Schimmack, Prof.
    Carlo Umiltà, Prof. Ettore Ambrosini, Dr. Filippo Gambarota, Dr.
    Giulia Calignano, Prof. Massimo Grassi, Prof. Livio Finos

### ONIRICAMENTE

Member of the **Organizing team** of the one-day workshop dedicated to
public outreach on the Psychology of Sleep. Padova (Italy)
(<https://sites.google.com/view/oniricamente/home-page?authuser=0>)

### Cognitive Neuroscience of Sleep Summer School

Member of the **Supporting team**. The Summer School examined methods
for investigating sleep and memory in humans and animals. It also
covered topics related to sleep medicine and dreaming. Nijmegen
(Netherlands)

\newpage

## Third Mission (Terza Missione)

```{r }
#| label: terzamissione
#| output: asis
#| echo: false
tibble::tribble(
    ~degree, ~institution, ~dates, ~details,
    "Science4all", "University of Padova, Italy", "2025",
     "Centra il bersaglio: tra misurazione, probabilità e incertezza. Activity organized by the Psicostat Research Group and proposed during the Science4All activity at the University of Padova (27-28th September 2025)"
) |>
  cvevents(when = "dates", what = "degree", where = "institution", details = "details")
```

## Research Groups Membership

```{r }
#| label: Groups
#| output: asis
#| echo: false
tibble::tribble(
    ~degree, ~institution, ~dates, ~details,
    "Psicostat", "University of Padova", "2024 - Present", 
      c("I am a core team member of Psicostat, an interdisciplinary research group specializing in quantitative psychology, psychometrics, psychological testing, and statistics.",
    "https://psicostat.dpss.psy.unipd.it/people.html"),
    "SleePy", "University of Padova", "2019 - Present", 
      c("I am a member of SleePy, a research group focusing on sleep psychology.")
) |>
  cvevents(when = "dates", what = "degree", where = "institution", details = "details")
```

## Collaborations

```{r }
#| label: Collaborations
#| output: asis
#| echo: false
tibble::tribble(
    ~degree, ~institution, ~dates, ~details,
    "Prof. Jelle Goeman", "Leiden University Medical Center, The Netherlands", "2025 - Present",
      c("Research on Bayesian approaches to the problem of multiplicity."),
    "Prof. Aldo Solari", "Ca’ Foscari University of Venice, Italy", "2025 - Present",
      c("Research on Bayesian approaches to the problem of multiplicity."),
    "Prof. Giovanni Parmigiani", "Harvard University", "2025 - Present",
      c("Research on Bayesian approaches to the problem of multiplicity."),
    "Dr. Bryant Jongkees", "Univerisity of Leiden, The Netherlands", "2024 - Present", 
      c("Research on the stability and flexibility dilemma in cognitive control."),
    "Dr. Antonino Visalli", "University of Modena-Reggio Emilia, Italy", "2023 - Present", 
      c("Research on computational models of learning and control.")
) |>
  cvevents(when = "dates", what = "degree", where = "institution", details = "details")
```

## Involvement in Research Groups

### National Project on Malpractice in Psychological Research

Collaborative initiative aimed at identifying and addressing
**methodological malpractice** in psychological science, with Enrico
Toffalini (University of Padova), Filippo Gambarota (University of
Padova) and Tommaso Feraco (University of Padova). My contributions
include:

-   Toffalini, E., **Calderan, M.**, Feraco, T., & Gambarota, F. Link
    Functions and Generalized Linear Models in Interaction Testing
    within Psychological Research. <https://osf.io/sjdu4>

-   Toffalini, E., **Calderan, M.**, Pagan, R., Tobia, V. &
    Sonuga-Barke, E. A Critical Tails or Types? A Critical Systematic
    Review of Taxometric Studies of Neurodevelopmental Conditions. Under
    review in *Journal of Child Psychology and Psychiatry*
    <https://github.com/EnricoToffalini/Taxometrics-Neurodevelopmental-Disorders/tree/main>

### National Project on Adaptive Cognitive Control in Children

Part of a national research group focused on investigating adaptive
cognitive control in typical, at-risk, and atypical populations within a
Neuroconstructivist framework, with Giovanni Mento (University of
Padova), Fiorella Del Popolo Cristaldi (University of Padova), Lisa
Toffoli (University of Padova), Giulia Stefanelli (University of
Padova), Gian Marco Duma (Epilepsy and Clinical Neurophysiology Unit,
IRCCS E. Medea). The group has contributed to multiple peer-reviewed
publications, conference presentations, and posters. My contributions
specifically focused on the application of **Bayesian methods**,
including **generalized multilevel models** and **survival analysis**
techniques, in the following selected works:

-   Toffoli, L., **Calderan, M.**, Del Popolo Cristaldi, F., Duma, G.
    M., Calcagnì, A., Pastore, M., Tarantino, V., & Mento, G. (2025).
    Can I afford one more candy? How motivational contexts shape
    adaptive cognitive control in children. *Developmental Psychology*.
    Advance online publication. <https://doi.org/10.1037/dev0001976>.

-   Stefanelli G., Toffoli L., **Calderan M.**, Del Popolo Cristaldi F.,
    Duma G. M., Tarantino V., Visalli A., Sellaro R., Mento G.
    Apprendimento associativo implicito e volatilità ambientale
    nell’ADHD. **Video-Poster** at Giornate di aggiornamento sull’uso
    degli strumenti in Psicologia Clinica dello Sviluppo Bologna
    (Italy), February 2025.

-   Stefanelli G., Toffoli L., **Calderan M.**, Duma G. M., Del Popolo
    Cristaldi F., Tarantino V., Visalli A., Sellaro R. & Mento G. Super
    Learning Bros: Developmental trajectories of probabilistic learning
    in volatile environment. **Talk** at the Cognitive Science Arena,
    Brixen (Italy), February 2025.

-   Toffoli, L.,**Calderan, M.**, Duma, G. M., Frisina, S., Tarantino
    V., & Mento, G. I'm talking to you! Interactive digital content
    effects on children's adaptive cognitive control. **Talk** at the
    Cognitive Science Arena, Brixen (Italy), February 2024.

-   Toffoli, L., **Calderan, M.**, Del Popolo Cristaldi, F., Duma, G.
    M., Calcagnì, A., Pastore, M., Tarantino, V., & Mento, G. Can I
    afford one more candy? How motivational contexts shape adaptive
    cognitive control in children. **Talk** at the Cognitive Science
    Arena, Brixen (Italy), February 2023.

\newpage

## Training

```{r}
#| label: Training
#| output: asis
#| echo: false
tibble::tribble(
    ~role, ~institution, ~dates, ~details, ~tasks,
    "Model-based Neuroscience Summer School", "University of Amsterdam, the Netherlands", "29/07/2024 - 02/08/2024",
    " ", c("Hands-on experience in both cognitive modeling using evidence-accumulation models and cognitive neuroscience methods. Three-day introduction to evidence-accumulation modeling using Bayesian inference. Two
days focused on how to use the evidence-accumulation framework to formalize performance in complex experimental paradigms, how to construct joint models of multiple tasks using techniques such as hierarchical factor models, and how to combine evidence-accumulation and reinforcement-learning models.", "Lecturers: Prof. Andrew Heathcote, Prof. Dora Matzke, Dr. Michael Nunez, Dr. Steven Miletic, and Dr. Niek Stevenson"), 
    "qHelp international seminar on Quantitative Psychology", "Arrifana, Portugal", "26/03/2023 - 02/04/2023",
    " ", c("A one-week intensive seminar covering Shiny and R Markdown for interactive data reporting, Copula theory and its applications in dependence modeling, numerical methods, and optimization techniques for computational analysis.", "Lecturers: Julian Mollenhauer, Ana Lourenço, Prof. Luciano Stefanutti, Prof. Hans Colonius, Prof. Francis Tuerlinckx, and Prof. Sérgio Moreira"
    ),
"Statistical Rethinking", "Online Course", "06/01/2023 - 10/03/2023",
    " ", c("Pre-recorded lectures and weekly meetings to discuss the material. This course teaches data analysis, focusing on scientific models: conceptual and causal models. Bayesian data analysis to connect scientific models to evidence.", "Lecturers: Prof. Richard McElreath"),
"Fundamentals and Applications of Pupillometry", "University of Padova, Italy", "20 hours",
    " ", c("This course offers an introduction to the use of pupillometry in cognitive science, combining practical exercises in data processing with free software tools: OpenSesame for implementing classic cognitive psychology tasks and R for analyzing and visualizing continuous pupil diameter changes. Covering key topics such as noise sources, experimental design, data processing options, and the cognitive interpretation of pupillometric measures.", "Professor: Dr. Giulia Calignano"),
    "EEGLAB: analysis of electroencephalographic data", "University of Padova, Italy", "20 hours",
    " ", c("The EEGLAB and ERPLAB toolboxes, which operate within MATLAB, facilitate the analysis of electroencephalographic (EEG) data. This course offers foundational skills in data analysis and theoretical knowledge through practical examples, covering key topics such as data pre-processing and event-related potential (ERP) computation.", "Professor: Dr. Mattia Doro"),
"Introduction to R", "University of Padova, Italy", "20 hours",
    " ", c("This course introduces the fundamentals of the open-source programming language R, teaching core programming concepts, data structures, and function creation through practical exercises to build versatile skills applicable across academic and professional settings.", "Professor: Dr. Filippo Gambarota"),
"PsychoPy3: experimental programming", "University of Padova, Italy", "20 hours",
    " ", c("This course introduces participants to PsychoPy, an open-source Python-based software for designing and running behavioral science experiments, teaching them how to create, test, deploy, and manage experiments using its flexible and user-friendly graphical interface.", "Professor: Dr. Thomas Quettier")) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```

\newpage

## Scientific Societies Membership

```{r }
#| label: Societies
#| output: asis
#| echo: false

tibble::tribble(
    ~degree, ~dates, ~institution,
    "Cognitive Science Society", "", "2024 - Present", 
    "Italian Reproduciblity Network",  "", "2023 - Present", 
    "European Sleep Research Society",  "", "2023 - Present", 
    "AIP, Sezione Sperimentale", "",  "2022 - Present", 
    "Society for the Improvement of Psychological Science",  "", "2022 - 2023", 
    "European Society for Cognitive Psychology",  "", "2021 - 2023"
    
) |>
  cvevents(when = "dates", what = "degree", where = "institution")

```

## Languages

```{r}
#| label: Languages 
#| output: asis
#| echo: false
tibble::tribble(
     ~role, ~institution, ~dates, ~details, ~tasks,
    "Italian", "Mother Tongue", " ",
    " ", c(),
    "English", "Proficient", " ",
    " ", c(),
    "Spanish", "Beginner", " ",
    " ", c()) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```

## Programming Languages

```{r}
#| label: Programming 
#| output: asis
#| echo: false
tibble::tribble(
     ~role, ~institution, ~dates, ~details, ~tasks,
    "R/R Studio", "Proficient", " ",
    " ", c(),
    "STAN", "Intermediate", " ",
    " ", c(),
    "JAGS", "Basic", " ",
    " ", c(),
     "Python", "Basic", " ",
    " ", c(),
    "MatLab", "Basic", " ",
    " ", c()) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```

\newpage

## Research and Project Management Skills

```{r}
#| label: skills
#| output: asis
#| echo: false
tibble::tribble(
     ~role, ~institution, ~dates, ~details, ~tasks,
    "PsychoPy/Pavlovia and OpenSesame/OSWeb", "Intermediate", " ",
    " ", c("Task development for behavioral research."),
    "GitHub and GitLab", "Intermediate", " ",
    " ", c("Version control and collaboration."),
     "Docker", "Basic", " ",
    " ", c("Development and deployment of containers."),
    "Google Suite, Office Suite", "Intermediate", " ",
    " ", c("Gmail, Calendar, Drive, Meet, Docs, Forms, Sheets.")) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")

```

## Operating Systems

```{r}
#| label: syst
#| output: asis
#| echo: false

tibble::tribble(
     ~role, ~institution, ~dates, ~details, ~tasks,
    "macOS", "Intermediate", " ",
    " ", c(),
    "Windows", "Intermediate", " ",
    " ", c(),
     "Linux", "Intermediate", " ",
    " ", c()) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```

------------------------------------------------------------------------

I authorize the processing of personal data included in my CV in accordance with Legislative
Decree 2018/101 and the GDPR (Regulation EU 2016/679).
I hereby declare that the information and details provided in this Curriculum Vitae are true
and accurate to the best of my knowledge, acknowledging the legal and criminal consequences
of providing false statements as per Article 76 of Presidential Decree 445/2000.

::: {.pdf .no-print}
</br>

<center>*Last update: `r Sys.Date()`*</center>

</br>
:::