---
format:
  html:
    toc: true
    toc-depth: 3
    toc-title: Section
    toc-location: right
    page-layout: full
    format-links: false
  pdf:
    output-file: cv-pdf   # keeps the same URL as before: docs/cv-pdf.pdf
    toc: false
    colorlinks: true
    linkcolor: accent
    urlcolor: accent
    margin-right: 1in
    margin-left: 1in
    margin-top: 1.15in
    margin-bottom: 1.25in
    # mainfont: "Avenir Next"   # uncomment to change the body font (any font installed on your Mac)
    include-in-header:
      text: |
        \usepackage{fontawesome5}
        \usepackage{academicons}
        % ---------- Style (easy to edit) ----------
        \usepackage{xcolor}
        % Accent color for headings and links: change the hex code here
        \definecolor{accent}{HTML}{1A5276}
        % Section headings: accent color, thin rule under main sections
        \usepackage{titlesec}
        \titleformat{\section}{\Large\bfseries\color{accent}}{}{0pt}{}[{\color{accent}\titlerule[0.6pt]}]
        \titleformat{\subsection}{\large\bfseries\color{accent}}{}{0pt}{}
        \titleformat{\subsubsection}{\normalsize\bfseries}{}{0pt}{}
        % Never leave a heading stranded at the bottom of a page
        \usepackage{needspace}
        \newcommand{\sectionbreak}{\needspace{5\baselineskip}}
        \newcommand{\subsectionbreak}{\needspace{4\baselineskip}}
        % Footer: name on the left, page number on the right
        \usepackage{fancyhdr}
        \fancyhf{}
        \renewcommand{\headrulewidth}{0pt}
        \fancyfoot[L]{\footnotesize\textcolor{gray}{Margherita Calderan — Curriculum Vitae}}
        \fancyfoot[R]{\footnotesize\textcolor{gray}{\thepage}}
        \pagestyle{fancy}
        \fancypagestyle{plain}{\fancyhf{}\renewcommand{\headrulewidth}{0pt}\fancyfoot[L]{\footnotesize\textcolor{gray}{Margherita Calderan — Curriculum Vitae}}\fancyfoot[R]{\footnotesize\textcolor{gray}{\thepage}}}
engine: knitr
editor:
  markdown:
    wrap: 72
---

::: {.content-visible when-format="pdf"}
\begin{center}
{\huge\bfseries\textcolor{accent}{Margherita Calderan, Ph.D.}}

\normalsize My research interests include computational models of cognition, Bayesian statistics, and metascience.

\faEnvelope\ \href{mailto:margherita.calderan@gmail.com}{margherita.calderan@gmail.com}\\[0.2em]
\faGithub\ \href{https://github.com/mar-cald}{github.com/mar-cald} \quad
\faGitlab\ \href{https://gitlab.pavlovia.org/mar.cald}{gitlab.pavlovia.org/mar.cald} \quad
\aiResearchGate\ \href{https://www.researchgate.net/profile/Margherita-Calderan-2}{ResearchGate} \quad
\aiOSF\ \href{https://osf.io/5ca9t/}{OSF}
\end{center}
:::

::: {.content-visible when-format="html"}
Download the [PDF](cv-pdf.pdf){target="_blank"} version.

*Last update: `r Sys.Date()`*
:::

```{r}
#| label: cvevents
#| echo: false

# One function, two outputs: HTML gets the styled two-column divs
# (see .cvevent in styles.css), PDF gets plain Markdown.
cvevents <- function(tbl, when, what, where, details = NULL) {
  result <- ""

  if (knitr::is_html_output()) {
    for (i in seq_len(nrow(tbl))) {
      block <- '<div class="cvevent">\n'
      block <- paste0(block, '  <div class="cvevent-left">\n')
      block <- paste0(block, '    <strong>', tbl[[what]][i], '</strong><br/>\n')
      if (nzchar(trimws(tbl[[where]][i]))) {
        block <- paste0(block, '    <em>', tbl[[where]][i], '</em><br/>\n')
      }

      if (!is.null(details)) {
        detail_items <- tbl[[details]][[i]]
        if (length(detail_items) > 0) {
          block <- paste0(block, '    <ul>\n')
          for (item in detail_items) {
            # Auto-link any URLs in item
            item <- gsub("(https?://[^\\s)]+)", "<a href='\\1' target='_blank' rel='noopener noreferrer'>\\1</a>", item, perl = TRUE)
            block <- paste0(block, '      <li>', item, '</li>\n')
          }
          block <- paste0(block, '    </ul>\n')
        }
      }

      block <- paste0(block, '  </div>\n')
      block <- paste0(block, '  <div class="cvevent-right">', tbl[[when]][i], '</div>\n')
      block <- paste0(block, '</div>\n\n')
      result <- paste0(result, block)
    }
  } else {
    for (i in seq_len(nrow(tbl))) {
      header <- paste0("**", tbl[[what]][i], "**  \n")
      institution <- if (nzchar(trimws(tbl[[where]][i]))) paste0("_", tbl[[where]][i], "_  \n") else ""
      date <- paste0(tbl[[when]][i], "\n")

      block <- paste0(header, institution, date)

      if (!is.null(details)) {
        detail_items <- tbl[[details]][[i]]
        if (length(detail_items) > 0) {
          block <- paste0(block, "\n")
          for (item in detail_items) {
            # Auto-link any URLs in item
            item <- gsub("(https?://[^\\s)]+)", "<\\1>", item, perl = TRUE)
            block <- paste0(block, "  - ", item, "\n")
          }
        }
      }
      block <- paste0(block, "\n")
      result <- paste0(result, block)
    }
  }

  knitr::asis_output(result)
}

```

------------------------------------------------------------------------

## Current Position

```{r}
#| label: present
#| output: asis
#| echo: false

tibble::tribble(
    ~role, ~institution, ~dates, ~details, ~tasks,
    "Research Assistant", "Department of Developmental Psychology and Socialization, University of Padova, Italy", "May 2026 - Present",
    " ", c("Number-space association: A comparative, developmental and neurobiological
approach", "PI: Prof. Silvia Benavides")) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```

## Research

```{r}
#| label: past
#| output: asis
#| echo: false

tibble::tribble(
    ~role, ~institution, ~dates, ~details, ~tasks,
    "Research Fellow", "Department of General Psychology, University of Padova, Italy", "Oct. 2024 - Mar. 2026", 
    " ", c("Tails or types? Testing the dimensional hypothesis in neurodevelopmental disorders", "Supervisor: Prof. Enrico Toffalini")) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```


## Education

```{r }
#| label: education
#| output: asis
#| echo: false
tibble::tribble(
    ~degree, ~institution, ~dates, ~details,
    "Ph.D. in Psychological Sciences - cum laude", "University of Padova, Italy", "Defense: Mar. 2025",
      c("Thesis: Balancing stability and flexibility in cognitive control and learning: the effects of arousal",
        "https://researchdata.cab.unipd.it/1437/",
        "Supervisor: Prof. Roberta Sellaro, Co-Supervisor: Prof. Nicola Cellini"),
     "Postgraduate Internship", "Psychophysiology Lab, University of Padova, Italy", "Jan. 2021 - Dec. 2021", c(
        "Investigated the role of sleep characteristics in false memory formation and emotional reactivity.",
        "Supervisors: Prof. Andrea Spoto, Prof. Nicola Cellini"),
    "M.Sc. in Cognitive Neuroscience and Clinical Neuropsychology - 110/110 cum laude", "University of Padova, Italy", "Oct. 2018 - Dec. 2020",
      c("Thesis: Sleep characteristics in adults with high functioning autism: a polysomnographic study", "Supervisor: Prof. Nicola Cellini"),
    "Curricular Internship", "Psychophysiology Lab, University of Padova, Italy", "Dec. 2019 - Aug. 2020", c(
        "Analyzed polysomnographic data to examine sleep architecture in young adults with high-functioning autism.",
        "Collaborated with the University of Trento and the University of Tübingen.",
        "Supervisor: Prof. Nicola Cellini"
    ),
    "B.Sc. in Cognitive Psychology and Psychobiology - 109/110", "University of Padova, Italy", "Sept. 2015 - Jul. 2018",
      c("Thesis: Gender differences in the long-term consolidation of emotional memories",
        "Supervisor: Prof. Michela Sarlo")
) |>
  cvevents(when = "dates", what = "degree", where = "institution", details = "details")
```

## Abroad

```{r}
#| label: Abroad
#| output: asis
#| echo: false
tibble::tribble(
    ~role, ~institution, ~dates, ~details, ~tasks,
    "Visiting Scholar", "Department of Biomedical Data Sciences, Leiden University Medical Center, the Netherlands", "1.5 months (Sept. 2025 - Oct. 2025)",
    "", c(
        "Research on Bayesian approaches to the problem of multiplicity.",
        "Supervisor: Prof. Jelle Goeman"
    ),
    "Visiting Ph.D. Student", "Cognitive Psychology Unit, University of Leiden, the Netherlands", "4 months (Feb. 2024 - Jun. 2024)",
    "", c(
        "Worked on a research project investigating how mind-wandering affects cognitive flexibility, applying computational models (https://psyarxiv.com/quhns) to analyze behavioral data.",
        "Supervisor: Dr. Bryant Jongkees"
    ),
         "Research Intern", "Donders Sleep and Memory Lab, Donders Institute, the Netherlands", "2 months (Jun. 2019 - Aug. 2019)",
    "", c(
        "Assisted with a project on the association between affective memory bias, medial prefrontal schema processing, and sleep in depressed patients and healthy controls.",
        "Assisted with a project on lucid dream induction.",
        "Supervisor: Prof. Martin Dresler"
    ),
    "Erasmus +", "Jaume I University, Spain", "5 months (Jan. 2017 - Jun. 2017)",
    " ", c("Completed a semester-long academic exchange as part of my undergraduate studies.")
    ) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```

## Publications

### Published

1. Feraco, T., **Calderan, M.** & Pellegrino, G. (2025).  The Living SEB Skills Project: A Living Resource for Review and Meta-Analysis of Social, Emotional, and Behavioral Skills. *European Journal of Personality*. <https://doi.org/10.1177/08902070261467477>.


2. Mazzoni, N., Kurz, E.V., Cellini, N., Ciringione, L., **Calderan, M.**, Gallitto, G., Falco, S., Venuti, P., Zinke, K., Born, J., & Carìa, A. (2026). Aperiodic and periodic neural activity during sleep in autism spectrum disorders. *BMC Medicine*. <https://doi.org/10.1186/s12916-026-04771-6>

3. **Calderan, M.**, Visalli, A., Degasperi, G., Toffoli, L., Sellaro,
    R., & Cellini, N. (2026). Predictions under sleep restriction: The effects
    of partial sleep deprivation on learning and inhibitory control.
    *Royal Society Open Science*. <https://doi.org/10.1098/rsos.252345>. 

4.  **Calderan, M.**, Jongkees, J.B., Gambarota, F., Pastore, M.,
    Cellini, N., & Sellaro, R. (2025). Isolating working memory gating processes
    under stress. *Collabra::Psychology*. <https://doi.org/10.1525/collabra.140750>.

5.  **Calderan, M.**, Toffalini, E., Mirandola, C., & Cellini, N.
    (2025). Sleep does not affect false memory production on a
    script-based test. *Neuropsychologia*.
    <https://doi.org/10.1016/j.neuropsychologia.2025.109210>.

6.  Toffoli, L., **Calderan, M.**, Del Popolo Cristaldi, F., Duma, G.
    M., Calcagnì, A., Pastore, M., Tarantino, V., & Mento, G. (2025).
    Can I afford one more candy? How motivational contexts shape
    adaptive cognitive control in children. *Developmental Psychology*.
    <https://doi.org/10.1037/dev0001976>.

7.  Sobol, M., Błachnio, A., **Calderan, M.**, Degasperi, G., Mioni, G.,
    Hryhorchuk, I., Plucińska, E., Stasiniewicz, J., Kwapiński, J.,
    Jankowski, K., & Cellini, N. (2025). Balanced time perspective as a
    factor mitigating the negative consequences of sleep disruptions in
    the perinatal period. *Chronobiology International*, 1–12.
    <https://doi.org/10.1080/07420528.2025.2490499>

8.  **Calderan, M.**, & Visalli, A. (2024). Challenges of meta-learning
    and rational analysis in large worlds. *Behavioral and Brain
    Sciences*, 47, e148.
    <https://doi.org/10.1017/S0140525X24000128>.


### Under Review

1. **Calderan, M.**, Gambarota, F., Toffalini, E., & Altoè, G., Adjusting the Probability of Direction for Multiple Testing. **Preprint:** <https://doi.org/10.31234/osf.io/8zwx2_v2>.

2. Barbiero, J., Zeilinga, K., **Calderan, M.**  & Mioni, G., The contribution of the cerebellum in time perception: A systematic review and meta-analyses.

3. Stefanelli, G., Toffoli, L., Del Popolo Cristaldi, F., Duma, G.M., **Calderan, M.**, ... & Mento, G. Growing Up in a Changing World: volatility-driven implicit associative learning throughout development.

4.  Visalli, A., Calistroni, F. M., **Calderan, M.**, Donnarumma, F., Zorzi, M., & Ambrosini, E. A computational framework for integrating Predictive processes with evidence Accumulation Models (PAM). **Preprint:** <https://doi.org/10.48550/arXiv.2411.13203>.

5.  Toffalini, E., **Calderan, M.**, Pagan, R., Tobia, V., & Sonuga-Barke, E. Tails or Types? A Critical Systematic Review of Taxometric Studies of Neurodevelopmental Conditions. **Preprint:** <https://osf.io/ys5ad/files/bem36>.



### Preregistration

1. Manente, M., Altoè, G., Alfarone, I., **Calderan, M.** (2026, July 14). Mapping Researcher Degrees of Freedom in Meta-Analyses of Randomized Controlled Trials of EMDR for PTSD: A Systematic Scoping Review. <https://osf.io/8hefb>

2.  Toffalini, E., **Calderan, M.**, Sità, L., Feraco, T., & Gambarota, F. Link
    Functions and Generalized Linear Models in Interaction Testing
    within Psychological Research. <https://osf.io/sjdu4>

3.  Sirota, M., Šrol, J., Lisi, M., Juanchich, M., Guglani, K.,
    Silverstein, P., … **Calderan, M.**, ... Schmidt, K. (2025, Jan.
    14). Mapping and Increasing Error Correction Behaviour in a
    Culturally Diverse Sample. **Preprint:**
    <https://doi.org/10.17605/OSF.IO/WN4VX>.
    
### In Preparation

1.  Toffoli, L., **Calderan, M.**, Stefanelli, G., Duma, G.M., Del Popolo Cristaldi, F., Duma, G., Pastore, M., Frisina, S., Tarantino, V., & Mento, G., I am talking to you! Engagement modulates the effects of digital content exposure on preschoolers’ adaptive cognitive control.

2. Bastianello, T., **Calderan, M.**, Loschiavo, A.G.M., Nascimben, C., Visibelli, E., Reoyo-Serrano, N., Altoè, G., & Benavides-Varela, S. Domestic Media Exposure Delays Attainment of Babbling in Infants While Adult Input Accelerates Progress.

3. Van Dooren, R., **Calderan, M.**, Sellaro, R., & Jongkees, J.B., Dynamic and contextual modulation of constraints on cognitive control.



### Published Abstract

1.  **Calderan, M.**, Visalli, A., Sellaro, R., & Cellini, N. (2024).
    Restless Sleep, Uncertain Minds: Learning and Inhibitory Control
    Under Partial Sleep Deprivation. Proceedings of the Annual Meeting
    of the Cognitive Science Society, 46.
    <https://escholarship.org/uc/item/65b2f0n7>.

2.  **Calderan, M.**, Visalli, A., Sellaro, R., & Cellini, N. (2024).
    The Effects of Partial Sleep Deprivation on Adaptive Cognitive
    Control. *Sleep Medicine*,
    <https://doi.org/10.1016/j.sleep.2023.11.156>.

3.  **Calderan, M.**, Visalli, A., Sellaro, R., & Cellini, N. (2024).
    Expecting the unexpected: a closer look at the effect of partial
    sleep deprivation on learning and inhibitory control. *Journal of
    Sleep Research*, <https://doi.org/10.1111/jsr.14291>.

4.  Baldassarri, A., Colombo, C., Bergamo, D., **Calderan, M.**,
    Varanini, A., Ferrentino, A., D’Atri, A., & Cellini, N. (2024).
    Exploring the impact of oscillatory events during a nap on emotional
    memory consolidation. *Journal of Sleep Research*,
    <https://doi.org/10.1111/jsr.14291>

## Conferences

1. Barbolan, S., Slaby, R., **Calderan, M.**, Knedlíková Wanková, V., & Bertamini, M. Emotional Responses to Renaissance Art: Differences Between Venetian and Bohemian Paintings. **Poster** accepted at the AIP - Experimental Section XXXII Conference, Venice (Italy), Sept. 2026.

2. **Toward Robust Replicability: Modern Perspectives and Methods**. Organizer: **Calderan, M.** Speakers: Alongi, E., Garofalo, S., **Calderan, M.**, Andreella, A. Moderator: Epifania, M.O. **Symposium** accepted for the AIP - Experimental Section XXXII Conference, Venice (Italy), Sept. 2026.

3. Barbolan, S., Slaby, R., **Calderan, M.**, Knedlíková Wanková, V., & Bertamini, M. Emotional Responses to Renaissance Painting: A Comparison Between Venetian and Bohemian Works. **Poster** accepted at the Visual Science of Art Conference (VSAC) 2026, Vision Forward: Perception, Art & Technology, London (United Kingdom), Aug. 2026.

4. Bastianello, T., Loschiavo, A., Nascimben, C., Reoyo-Serrano, N., **Calderan, M.**, Altoè, G., & Benavides-Varela, S. The effects of TV and electronic devices on language: a longitudinal study. **Poster** accepted at the ICIS 2026 (Panama), Jul. 2026.

5. Bastianello, T., **Calderan, M.**, Loschiavo, A., Nascimben, C., Visibelli, E., Reoyo-Serrano, N., Altoè, G., & Benavides-Varela, S. (2026). L’esposizione ai media rallenta il raggiungimento del babbling e l’input dell’adulto ne accelera il progresso. **Talk** at CLASTA, Torino (Jun. 2026).

6. Barbolan, S., Slaby, R., **Calderan, M.**, Knedlíková Wanková, V., & Bertamini, M. Emotional and Aesthetic Experience in Venetian and Bohemian Paintings from the Renaissance. **Poster** presented at the International Association of Empirical Aesthetics (IAEA) 2026 Conference, Future Follows Past – Creating a Gesamtkunstwerk together for Arts and Aesthetics Research, Jena (Germany), May 2026.


7.  Stefanelli G., Toffoli L., **Calderan M.**, Del Popolo Cristaldi F.,
    Duma G. M., Tarantino V., Visalli A., Sellaro R., Mento G.
    Apprendimento associativo implicito e volatilità ambientale
    nell’ADHD. **Video-Poster** at Giornate di aggiornamento sull’uso
    degli strumenti in Psicologia Clinica dello Sviluppo, Bologna
    (Italy), Feb. 2025.

8.  Stefanelli G., Toffoli L., **Calderan M.**, Duma G. M., Del Popolo
    Cristaldi F., Tarantino V., Visalli A., Sellaro R. & Mento G. Super
    Learning Bros: Developmental trajectories of probabilistic learning
    in volatile environment. **Talk** at the Cognitive Science Arena,
    Brixen (Italy), Feb. 2025.

9.  **Calderan, M.**, Visalli, A., Degasperi, G., Calistroni, F.M.,
    Sellaro, R., & Cellini, N. Expecting the unexpected: a closer look
    at the effect of partial sleep deprivation on learning and inhibitory
    control. **Poster** presented at Sleep Europe 2024, Seville (Spain),
    Sept. 2024.

10.  **Calderan, M.**, Visalli, A., Degasperi, G., Calistroni, F.M.,
    Sellaro, R., & Cellini, N. Restless Sleep, Uncertain Minds: Learning
    and Inhibitory Control Under Partial Sleep Deprivation. **Poster**
    presented at CogSci 2024: Dynamics of Cognition, Rotterdam
    (Netherlands), Jul. 2024.
11.  Degasperi, G., **Calderan, M.**, Mioni, G., Meisner, M., Blachnio,
    A., Hryhorchuk, I., Plucinska, E., Sobol, M., & Cellini, N. The role
    of sleep, circadian rhythms, balanced time perspective on perinatal
    depression symptoms. **Poster** at the Cognitive Science Arena,
    Brixen (Italy), Feb. 2024.

12.  Toffoli, L., **Calderan, M.**, Duma, G. M., Frisina, S., Tarantino
    V., & Mento, G. I'm talking to you! Interactive digital content
    effects on children's adaptive cognitive control. **Talk** at the
    Cognitive Science Arena, Brixen (Italy), Feb. 2024.

13.  **Calderan, M.**, Visalli, A., Sellaro, R., & Cellini, N. The
    Effects of Partial Sleep Deprivation on Adaptive Cognitive Control.
    **Poster** presented at World Sleep Congress, Rio de Janeiro
    (Brazil), Oct. 2023.

14.  **Calderan, M.**, Visalli, A., Sellaro, R., & Cellini, N. The
    sleep-deprived predictive brain: modeling the effect of partial sleep
    deprivation on adaptive cognitive control. **Talk** at the XXIX
    Conference of the Italian Association of Psychology (AIP) -
    Experimental Psychology Section. Lucca (Italy), Sept. 2023.

15.  **Calderan, M.**, Cellini, N., Sellaro, R., Stressed Minds:
    Unraveling Acute-Stress Effects on Working Memory Processes.
    **Mini-Talk** at the Cognitive Science Arena, Brixen (Italy),
    Feb. 2023.

16. Toffoli, L., **Calderan, M.**, Del Popolo Cristaldi, F., Duma, G.
    M., Calcagnì, A., Pastore, M., Tarantino, V., & Mento, G. Can I
    afford one more candy? How motivational contexts shape adaptive
    cognitive control in children. **Talk** at the Cognitive Science
    Arena, Brixen (Italy), Feb. 2023.

17. **Calderan, M.**, Cellini, N., Sellaro, R., Exploring the Influence
    of Stress on Working Memory Gating Mechanisms. **Mini-Talk** at the
    XXX Conference of the Italian Association of Psychology (AIP).
    Padova (Italy), Sept. 2022.

18. **Calderan, M.**, Cellini, N., Sellaro, R., Understanding
    stress-induced Effects on Working Memory gating mechanisms.
    **Poster** presented at the 22nd meeting of the European Society for
    Cognitive Psychology (ESCoP), Lille (France), Aug. 2022.


### Pre-conference workshops

-   **Generalized Linear Models for Psychology: Understanding, Simulating, and Planning Your Analyses**. Pre-conference Workshop Cognitive Science Arena, Brixen (Italy). Feb. 2026 (4 hrs.). Hands-on methodological workshop held with Filippo Gambarota, PhD. <https://psicostat.github.io/glm-workshop/>


-  **A Practical Introduction to Evidence Accumulation Models in Visual Perception Research**. European Conference on Visual Perception, Mainz (Germany). Aug. 2025 (2.5 hrs.). Hands-on methodological workshop held with Carolina Maria Oletto, PhD.
    <https://mar-cald.github.io/eam-workshop/eam-home.html>.

-  **Introduction to Reproducible Science**. Pre-School workshop
    *Replicability Crisis in Science*, Padova (Italy). Ed. 2025 and 2026 (2 hrs.). Material: <https://github.com/Mar-Cald/repro-pre-school>.


## Invited talks

-  **Bayesian inference and multiple comparisons: From idealization of methods to conscious practice**. **C**ognitive **N**euroscience **S**eminars, Department of General Psychology,  University of Padova, Italy. Dec. 2025.

-   **From Cognitive Psychology to Bayesian Multiple Testing**. Medical Statistics Meeting, Department of Biomedical Data Sciences, Leiden University Medical Center, Leiden, The Netherlands. Oct. 2025.

-   **Bayesian Multiple Testing**. STAT-Talk Series, Methodology and
    Statistics Department, Institute of Psychology, Leiden University,
    Leiden, The Netherlands. Sept. 2025.



## Awards and Grants

-  **Travel Grant**: Cognitive Science Arena, Brixen (Italy).
-   **Travel Grant**: European Conference on Visual Perception, Mainz (Germany).
-   **Travel Grant**: qHelp international seminar on Quantitative
    Psychology, Arrifana (Portugal).
-   **Painter Award**: Best Poster, Cognitive Science Arena, Brixen (Italy).
-   **Erasmus Placement Grant (2 Months)**: Donders Sleep and Memory
    Lab, Nijmegen (The Netherlands).
-   **Erasmus Placement Grant (5 Months)**: Jaume I University,
    Castellón de la Plana (Spain).

## Peer Reviews

Ad hoc reviewer (4 reviewed papers) for:

- Italian Journal of Applied Statistics (1)
- Frontiers in Psychology - Theoretical and Philosophical Psychology (1)
- Frontiers in Psychology - Cognition (1)
- PLoS ONE (1)

## Teaching

[planned] means that the course has been officially scheduled but not delivered yet.

### Lectures on contract (docenze a contratto)

- **Inferenza e statistica Bayesiana** (10 hours). Master in Quantitative Psychology, Department of Philosophy, Sociology, Education and Applied Psychology, University of Padova. Jul. 2026 [planned].

- **Modelli lineari** (10 hours). Master in Quantitative Psychology, Department of Philosophy, Sociology, Education and Applied Psychology, University of Padova. Jun. 2026 [planned].
Material: <https://mar-cald.github.io/psqt/modelli-lineari.html>

-   **Test per le organizzazioni** (21 hours, 3 CFU). 2nd semester of the 2025/2026 academic year. Lecturer (titolare di
    modulo) for the Master’s Degree in Psicologia Sociale, del Lavoro e
    della Comunicazione, University of Padova.
    Material: <https://ottaviae.github.io/test-organizzioni-fisppa/>

-   **Introduction to meta-analysis with application in R** (5 hours, 1
    CFU). Professor for the course within the PhD program in Psychological Sciences, University of Padova. Apr. 2026.
    Material: <https://mar-cald.github.io/meta-phd/>

### Seminars


- **Introduction to Bayesian Statistics with R and Stan** (30 hrs.). Intensive course on Bayesian statistics organized by the Italian Psychological Association (AIP). CEUB, Bertinoro (Italy), Jun. - Jul. 2026 [planned].


-   **Introduction to R**. An intensive R programming course offered
    within the ARCA (Applied Research Course Academy) courses,
    Department of Developmental Psychology and Socialization, University
    of Padova. Material: <https://github.com/arca-dpss/course-R-2425>
    -   Dec. 2024 (20 hrs.)
    -   Apr. 2025 (20 hrs.)
    -   Nov. 2025 (20 hrs.)
    -   Mar. 2026 (20 hrs.)
-   **Learning in Dynamic Environments: A Tentative Implementation of
    the Volatile Kalman Filter in Stan.** Presentation (1 hr.) on a
    Bayesian-based implementation of a learning algorithm for the
    2023/24 Psicostat meeting series:
    <https://psicostat.dpss.psy.unipd.it/meetings/slides/2024-03-22_calderan.pdf>

### Integrative teaching (Didattica integrativa)

-   **Assistance** during lectures for the course **Testing
    Psicologico** (Prof. Tatiana Marci), Bachelor's degree in Scienze psicologiche dello sviluppo, della personalità e delle relazioni interpersonali, University of Padova (14 hrs.).

-   Preparation and correction of **practical group exercises** and
    exams for the course **Experimental Research Methods in Psychology**
    (Prof. Roberta Sellaro), Master's degree in Developmental and
    Educational Psychology, University of Padova (14 hrs.).

-   **Assistance** in the preparation of exercises and corrections for
    the course **General Psychology** (Prof. Enrico Toffalini),
    Bachelor's degree in Techniques and Methods in Psychological
    Sciences, University of Padova (15 hrs.).

-   **Assistance** during lectures and preparation of **practical group
    exercise** for the course **General Psychology** (Prof. Giovanna
    Mioni), Bachelor's degree in Social and Work Psychological Sciences,
    University of Padova (14 hrs.).

### Workshops

-  **Bayesian Approaches To Multiplicity**. Psicostat HandZone on Bayesian Approaches To Multiplicity, University of Padova, Padova (Italy). Dec. 2025 (1.5 hrs.). <https://psicostat.dpss.psy.unipd.it/pages/handzone.html>


-  **Tempi di risposta**. Workshop on reaction time distributions,
    University of Padova, Padova (Italy). Jun. 2025 (1 hr.).
    Material: <https://mar-cald.github.io/tempi/>,
    <https://psicostat.dpss.psy.unipd.it/pages/handzone.html>


## Academic Roles

-  **Expert (Cultore della Materia) of Psychometrics (PSIC-01/C ex M-PSI/03)**
Department of Developmental Psychology and Socialization, University of Padova, Italy. Jan. 2026 - Present.

-   **Representative of Research Fellows** in the Department of General
    Psychology, University of Padova. Feb. 2025 - Mar. 2026

-   **Co-supervision of students** for their internships and
    Bachelor’s (2) and Master’s theses (1)

## Organizational Activities

### Methodological School: Replicability Crisis in Science

Member of the **Organizing team**. The school covers the epistemological, philosophical, and statistical foundations of replicability
(<https://psicostat.github.io/replicability-psy-unipd-phd>).

- Jun. 2025, Padova (Italy)
- May 2026, Padova (Italy)

-   **Lecturers**: Prof. Branden Fitelson, Prof. Giovanni Parmigiani,
    Dr. Filippo Gambarota, Dr. Margherita Calderan (ed. 2026)

### International Winter School - The 4 Ms: Meta-research, Measurement, Multi-lab, and Multiverse data analysis in Behavioral Sciences

Member of the **Organizing team**. The Winter School aims to introduce
attendees to advancements in meta-research, providing both theoretical
insights and practical tools to conduct rigorous research. Feb. 2025, Padova
(Italy). (<https://winterschool4ms.dpg.unipd.it/>)

-   **Lecturers**: Prof. Daniël Lakens, Prof. Dorothy Bishop, Prof.
    Jessica Flake, Prof. Lisa DeBruine, Prof. Ulrich Schimmack, Prof.
    Carlo Umiltà, Prof. Ettore Ambrosini, Dr. Filippo Gambarota, Dr.
    Giulia Calignano, Prof. Massimo Grassi, Prof. Livio Finos

### ONIRICAMENTE

Member of the **Organizing team** of the one-day workshop dedicated to
public outreach on the Psychology of Sleep. Jun. 2024, Padova (Italy)
(<https://sites.google.com/view/oniricamente/home-page?authuser=0>)

### Cognitive Neuroscience of Sleep Summer School

Member of the **Supporting team**. The Summer School examined methods
for investigating sleep and memory in humans and animals. It also
covered topics related to sleep medicine and dreaming. Nijmegen
(Netherlands)

## Third Mission (Terza Missione)

```{r }
#| label: terzamissione
#| output: asis
#| echo: false
tibble::tribble(
    ~degree, ~institution, ~dates, ~details,

     "Replicability Crisis in Science – Methodological Seminars", "University of Padova, Italy", "2025", "The school aims to provide a broad
and interdisciplinary perspective on replicability, along with tools
that help participants explore aspects most relevant to their own field.
Lectures cover the epistemological, philosophical, and statistical
foundations of replicability and the so-called replication crisis (Jun. 2025).",

    "Science4all", "University of Padova, Italy", "2025",
     "Centra il bersaglio: tra misurazione, probabilità e incertezza. Activity organized by the Psicostat Research Group and proposed during the Science4All activity at the University of Padova (Sept. 2025)",

"ONIRICAMENTE", "University of Padova, Italy", "2024",
     "One-day workshop dedicated to public outreach on the Psychology of Sleep (Jun. 2024)"
) |>
  cvevents(when = "dates", what = "degree", where = "institution", details = "details")
```

## Research Groups Membership

```{r }
#| label: Groups
#| output: asis
#| echo: false
tibble::tribble(
    ~degree, ~institution, ~dates, ~details,
    "Psicostat", "University of Padova", "2024 - Present",
      c("I am a core team member of Psicostat, an interdisciplinary research group specializing in quantitative psychology, psychometrics, psychological testing, and statistics.",
        "https://psicostat.dpss.psy.unipd.it/people.html"),
    "SleePy", "University of Padova", "2019 - Present",
      c("I am a member of SleePy, a research group focusing on sleep psychology.")
) |>
  cvevents(when = "dates", what = "degree", where = "institution", details = "details")
```

## Collaborations

```{r }
#| label: Collaborations
#| output: asis
#| echo: false
tibble::tribble(
    ~degree, ~institution, ~dates, ~details,
    "Prof. Jelle Goeman", "Leiden University Medical Center, The Netherlands", "2025 - Present",
      c("Research on Bayesian approaches to the problem of multiplicity."),
    "Prof. Aldo Solari", "Ca’ Foscari University of Venice, Italy", "2025 - Present",
      c("Research on Bayesian approaches to the problem of multiplicity."),

    "Prof. Giovanni Parmigiani", "Harvard University", "2025 - Present",
      c("Research and teaching projects about replicability in Psychology and Biomedical sciences."),

    "Prof. Branden Fitelson", "Northeastern University", "2025 - Present",
      c("Research and teaching projects about replicability in Psychology and Biomedical sciences."),

    "Dr. Bryant Jongkees", "Leiden University, The Netherlands", "2024 - Present",
      c("Research on stability and flexibility in cognitive control."),

    "Dr. Antonino Visalli", "University of Modena and Reggio Emilia, Italy", "2023 - Present",
      c("Research on computational models of learning and control.")
) |>
  cvevents(when = "dates", what = "degree", where = "institution", details = "details")
```

## Involvement in Research Groups

### National Project on Malpractice in Psychological Research

Collaborative initiative aimed at identifying and addressing
**methodological malpractice** in psychological science, with Enrico
Toffalini (University of Padova), Filippo Gambarota (University of
Padova) and Tommaso Feraco (University of Padova). My contributions
include:

-   Toffalini, E., **Calderan, M.**, Feraco, T., & Gambarota, F. Link
    Functions and Generalized Linear Models in Interaction Testing
    within Psychological Research. <https://osf.io/sjdu4>

-   Toffalini, E., **Calderan, M.**, Pagan, R., Tobia, V., &
    Sonuga-Barke, E. Tails or Types? A Critical Systematic
    Review of Taxometric Studies of Neurodevelopmental Conditions. Under
    review in *JCPP Advances*.
    <https://github.com/EnricoToffalini/Taxometrics-Neurodevelopmental-Disorders/tree/main>

### National Project on Adaptive Cognitive Control in Children

Part of a national research group focused on investigating adaptive
cognitive control in typical, at-risk, and atypical populations within a
Neuroconstructivist framework, with Giovanni Mento (University of
Padova), Fiorella Del Popolo Cristaldi (University of Padova), Lisa
Toffoli (University of Padova), Giulia Stefanelli (University of
Padova), Gian Marco Duma (Epilepsy and Clinical Neurophysiology Unit,
IRCCS E. Medea). The group has contributed to multiple peer-reviewed
publications, conference presentations, and posters. My contributions
specifically focused on the application of **Bayesian methods**,
including **generalized multilevel models** and **survival analysis**
techniques, in the following selected works:

-   Toffoli, L., **Calderan, M.**, Del Popolo Cristaldi, F., Duma, G.
    M., Calcagnì, A., Pastore, M., Tarantino, V., & Mento, G. (2025).
    Can I afford one more candy? How motivational contexts shape
    adaptive cognitive control in children. *Developmental Psychology*.
    Advance online publication. <https://doi.org/10.1037/dev0001976>.

-   Stefanelli G., Toffoli L., **Calderan M.**, Del Popolo Cristaldi F.,
    Duma G. M., Tarantino V., Visalli A., Sellaro R., Mento G.
    Apprendimento associativo implicito e volatilità ambientale
    nell’ADHD. **Video-Poster** at Giornate di aggiornamento sull’uso
    degli strumenti in Psicologia Clinica dello Sviluppo, Bologna
    (Italy), Feb. 2025.

-   Stefanelli G., Toffoli L., **Calderan M.**, Duma G. M., Del Popolo
    Cristaldi F., Tarantino V., Visalli A., Sellaro R. & Mento G. Super
    Learning Bros: Developmental trajectories of probabilistic learning
    in volatile environment. **Talk** at the Cognitive Science Arena,
    Brixen (Italy), Feb. 2025.

-   Toffoli, L., **Calderan, M.**, Duma, G. M., Frisina, S., Tarantino
    V., & Mento, G. I'm talking to you! Interactive digital content
    effects on children's adaptive cognitive control. **Talk** at the
    Cognitive Science Arena, Brixen (Italy), Feb. 2024.

-   Toffoli, L., **Calderan, M.**, Del Popolo Cristaldi, F., Duma, G.
    M., Calcagnì, A., Pastore, M., Tarantino, V., & Mento, G. Can I
    afford one more candy? How motivational contexts shape adaptive
    cognitive control in children. **Talk** at the Cognitive Science
    Arena, Brixen (Italy), Feb. 2023.

## Training

```{r}
#| label: Training
#| output: asis
#| echo: false
tibble::tribble(
    ~role, ~institution, ~dates, ~details, ~tasks,
    "Model-based Neuroscience Summer School", "University of Amsterdam, the Netherlands", "Jul. - Aug. 2024",
    " ", c("Hands-on experience in both cognitive modeling using evidence-accumulation models and cognitive neuroscience methods. Three-day introduction to evidence-accumulation modeling using Bayesian inference. Two
days focused on how to use the evidence-accumulation framework to formalize performance in complex experimental paradigms, how to construct joint models of multiple tasks using techniques such as hierarchical factor models, and how to combine evidence-accumulation and reinforcement-learning models.", "Lecturers: Prof. Andrew Heathcote, Prof. Dora Matzke, Dr. Michael Nunez, Dr. Steven Miletic, and Dr. Niek Stevenson"),
    "qHelp international seminar on Quantitative Psychology", "Arrifana, Portugal", "Mar. - Apr. 2023",
    " ", c("A one-week intensive seminar covering Shiny and R Markdown for interactive data reporting, Copula theory and its applications in dependence modeling, numerical methods, and optimization techniques for computational analysis.", "Lecturers: Julian Mollenhauer, Ana Lourenço, Prof. Luciano Stefanutti, Prof. Hans Colonius, Prof. Francis Tuerlinckx, and Prof. Sérgio Moreira"
    ),
"Statistical Rethinking", "Online Course", "Jan. - Mar. 2023",
    " ", c("Pre-recorded lectures and weekly meetings to discuss the material. This course teaches data analysis, focusing on scientific models: conceptual and causal models. Bayesian data analysis to connect scientific models to evidence.", "Lecturer: Prof. Richard McElreath"),
"Fundamentals and Applications of Pupillometry", "University of Padova, Italy", "20 hours",
    " ", c("This course offers an introduction to the use of pupillometry in cognitive science, combining practical exercises in data processing with free software tools: OpenSesame for implementing classic cognitive psychology tasks and R for analyzing and visualizing continuous pupil diameter changes. Covering key topics such as noise sources, experimental design, data processing options, and the cognitive interpretation of pupillometric measures.", "Professor: Dr. Giulia Calignano"),
    "EEGLAB: analysis of electroencephalographic data", "University of Padova, Italy", "20 hours",
    " ", c("The EEGLAB and ERPLAB toolboxes, which operate within MATLAB, facilitate the analysis of electroencephalographic (EEG) data. This course offers foundational skills in data analysis and theoretical knowledge through practical examples, covering key topics such as data pre-processing and event-related potential (ERP) computation.", "Professor: Dr. Mattia Doro"),
"Introduction to R", "University of Padova, Italy", "20 hours",
    " ", c("This course introduces the fundamentals of the open-source programming language R, teaching core programming concepts, data structures, and function creation through practical exercises to build versatile skills applicable across academic and professional settings.", "Professor: Dr. Filippo Gambarota"),
"PsychoPy3: experimental programming", "University of Padova, Italy", "20 hours",
    " ", c("This course introduces participants to PsychoPy, an open-source Python-based software for designing and running behavioral science experiments, teaching them how to create, test, deploy, and manage experiments using its flexible and user-friendly graphical interface.", "Professor: Dr. Thomas Quettier")) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```

## Scientific Societies Membership

```{r }
#| label: Societies
#| output: asis
#| echo: false

tibble::tribble(
    ~degree, ~dates, ~institution,
    "AIP, Sezione Sperimentale", "2022 - Present", "",
    "Italian Reproducibility Network", "2023 - Present", "",
    "Cognitive Science Society", "2024 - 2025", "",
    "European Sleep Research Society", "2023 - 2025", "",
    "Society for the Improvement of Psychological Science", "2022 - 2023", "",
    "European Society for Cognitive Psychology", "2021 - 2023", ""

) |>
  cvevents(when = "dates", what = "degree", where = "institution")

```

## Languages

::: {.content-visible when-format="html"}
🇮🇹 Italian: Mother Tongue\
🇬🇧 English: Proficient\
🇪🇸 Spanish: Beginner
:::

::: {.content-visible unless-format="html"}

```{r}
#| label: Languages
#| output: asis
#| echo: false
tibble::tribble(
     ~role, ~institution, ~dates, ~details, ~tasks,
    "Italian", "Mother Tongue", " ",
    " ", c(),
    "English", "Proficient", " ",
    " ", c(),
    "Spanish", "Beginner", " ",
    " ", c()) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```

:::

## Programming Languages

```{r}
#| label: Programming
#| output: asis
#| echo: false
tibble::tribble(
     ~role, ~institution, ~dates, ~details, ~tasks,
    "R / RStudio", "Proficient", " ",
    " ", c(),
    "Stan", "Intermediate", " ",
    " ", c(),
    "JAGS", "Basic", " ",
    " ", c(),
     "Python", "Basic", " ",
    " ", c(),
    "MATLAB", "Basic", " ",
    " ", c()) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```

## Research and Project Management Skills

```{r}
#| label: skills
#| output: asis
#| echo: false
tibble::tribble(
     ~role, ~institution, ~dates, ~details, ~tasks,
    "PsychoPy/Pavlovia and OpenSesame/OSWeb", "Intermediate", " ",
    " ", c("Task development for behavioral research."),
    "GitHub and GitLab", "Intermediate", " ",
    " ", c("Version control and collaboration.", "https://github.com/Mar-Cald, https://gitlab.pavlovia.org/mar.cald"),
     "Docker", "Basic", " ",
    " ", c("Development and deployment of containers."),
    "Google Suite, Office Suite", "Intermediate", " ",
    " ", c("Gmail, Calendar, Drive, Meet, Docs, Forms, Sheets.")) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")

```


## R Packages

- *multibayes*: tools for Bayesian multiplicity adjustments (**maintainer**). <https://mar-cald.github.io/multibayes/>

## Operating Systems

```{r}
#| label: syst
#| output: asis
#| echo: false

tibble::tribble(
     ~role, ~institution, ~dates, ~details, ~tasks,
    "macOS", "Intermediate", " ",
    " ", c(),
    "Windows", "Intermediate", " ",
    " ", c(),
     "Linux", "Intermediate", " ",
    " ", c()) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```

------------------------------------------------------------------------

::: {.content-visible when-format="pdf"}
\footnotesize

I authorize the processing of personal data included in my CV in accordance with Legislative
Decree 101/2018 and the GDPR (Regulation EU 2016/679).
I hereby declare that the information and details provided in this Curriculum Vitae are true
and accurate to the best of my knowledge, acknowledging the legal and criminal consequences
of providing false statements as per Article 76 of Presidential Decree 445/2000.

\begin{center}
\textit{Last update: `r Sys.Date()`}
\end{center}
:::
