---
format:
  html:
    toc: true
    toc-depth: 3
    toc-title: Section
    toc-location: right
    page-layout: full
    format-links: false
    body-classes: cv-page
  pdf:
    output-file: cv-pdf   # keeps the same URL as before: docs/cv-pdf.pdf
    toc: false
    colorlinks: true
    linkcolor: accent
    urlcolor: accent
    fontsize: 10pt
    # The page starts at "##", so shift everything up one level: "##" becomes
    # a LaTeX \section, "###" a \subsection. Without this the headings below
    # would be styled as sub-headings and lose their rule.
    shift-heading-level-by: -1
    # The body font. Any font installed on this Mac works; remove the line
    # to go back to LaTeX's own font. (Rendering on a computer that does not
    # have this font will fail, so change it if you move the site elsewhere.)
    mainfont: "Avenir Next"
    margin-right: 0.9in
    margin-left: 0.9in
    margin-top: 1in
    margin-bottom: 1.1in
    include-in-header:
      text: |
        % All the little symbols come from Font Awesome. (The academicons
        % package was dropped: the copy of its font on this machine is missing
        % the ORCID, ResearchGate and OSF symbols, so they printed as nothing.)
        \usepackage{fontawesome5}

        % ---------- Colours (easy to edit) ----------
        \usepackage{xcolor}
        % Accent colour for headings and links.
        % It is the same purple as the website (see _brand.yml and styles.css).
        \definecolor{accent}{HTML}{6E0748}
        \definecolor{cvgrey}{HTML}{6C757D}   % dates and other small print

        % ---------- Long web addresses break tidily instead of overflowing ----------
        \usepackage{xurl}

        % ---------- No stretched word spacing ----------
        % ragged2e (not plain \raggedright) so that \hfill still pushes the
        % dates all the way to the right margin.
        \usepackage[document]{ragged2e}

        % ---------- Section headings ----------
        % Quarto builds the PDF with the KOMA-Script class, which ignores the
        % titlesec package, so the headings are set up the KOMA way instead.
        \addtokomafont{section}{\color{accent}\large\bfseries}
        \addtokomafont{subsection}{\color{accent}\normalsize\bfseries}
        \addtokomafont{subsubsection}{\color{accent}\small\bfseries}
        % space before / after each heading
        \RedeclareSectionCommand[beforeskip=-1.7em, afterskip=0.7em]{section}
        \RedeclareSectionCommand[beforeskip=-1.1em, afterskip=0.4em]{subsection}
        \RedeclareSectionCommand[beforeskip=-0.9em, afterskip=0.3em]{subsubsection}
        % a thin rule under the main section headings only
        \renewcommand*{\sectionlinesformat}[4]{%
          \Ifstr{#1}{section}
            {\parbox{\linewidth}{\raggedsection#3#4\\[0.25em]{\color{accent!30}\rule{\linewidth}{0.7pt}}}}
            {#3#4}%
        }

        % ---------- Lists: tighter, with a small accent-coloured bullet ----------
        \usepackage{enumitem}
        \setlist[itemize]{leftmargin=1.1em, topsep=0.25em, itemsep=0.15em,
                          parsep=0pt, label=\textcolor{accent!70}{\small\textbullet}}
        \setlist[enumerate]{leftmargin=1.7em, topsep=0.35em, itemsep=0.4em, parsep=0pt}

        % ---------- The date, pushed to the right of an entry ----------
        % \mbox keeps the date in one piece: if the title is long the whole
        % date moves to the next line instead of being cut in two.
        \newcommand{\cvdate}[1]{\hfill\mbox{\small\color{cvgrey}#1}}

        % ---------- The thin rule under the name at the top ----------
        \newcommand{\cvrule}{\vspace{0.7em}\noindent{\color{accent!30}\rule{\linewidth}{0.7pt}}\vspace{0.2em}}

        % ---------- Never leave a heading stranded at the bottom of a page ----------
        \usepackage{needspace}
        \AddToHook{cmd/section/before}{\needspace{8\baselineskip}}
        \AddToHook{cmd/subsection/before}{\needspace{5\baselineskip}}

        % ---------- Footer: name on the left, page number on the right ----------
        \usepackage{fancyhdr}
        \fancyhf{}
        \renewcommand{\headrulewidth}{0pt}
        \fancyfoot[L]{\footnotesize\color{cvgrey}Margherita Calderan — Curriculum Vitae}
        \fancyfoot[R]{\footnotesize\color{cvgrey}\thepage}
        \pagestyle{fancy}
        \fancypagestyle{plain}{\fancyhf{}\renewcommand{\headrulewidth}{0pt}\fancyfoot[L]{\footnotesize\color{cvgrey}Margherita Calderan — Curriculum Vitae}\fancyfoot[R]{\footnotesize\color{cvgrey}\thepage}}
engine: knitr
editor:
  markdown:
    wrap: 72
---

```{r}
#| label: setup
#| include: false

# Everything below comes from the spreadsheets in data/ .
# To update the CV, edit those files — you do not need to touch this page.
# See data/README.md for instructions.
source("_cv-helpers.R")
```

::: {.content-visible when-format="pdf"}
\begin{center}
{\LARGE\bfseries\color{accent}Margherita Calderan, Ph.D.}\\[0.5em]
{\small\color{cvgrey}My research interests include computational models of cognition, Bayesian statistics, and metascience.}\\[0.9em]
{\footnotesize
\faEnvelope\ \href{mailto:margherita.calderan@gmail.com}{margherita.calderan@gmail.com} \quad
\faOrcid\ \href{https://orcid.org/0009-0005-5668-5162}{0009-0005-5668-5162}\\[0.35em]
\faGithub\ \href{https://github.com/mar-cald}{github.com/mar-cald} \quad
\faGitlab\ \href{https://gitlab.pavlovia.org/mar.cald}{gitlab.pavlovia.org/mar.cald} \quad
\faResearchgate\ \href{https://www.researchgate.net/profile/Margherita-Calderan-2}{ResearchGate} \quad
\faSpa\ \href{https://osf.io/5ca9t/}{OSF}
}
\end{center}
\cvrule
:::

::: {.content-visible when-format="html"}
Download the [PDF](cv-pdf.pdf){target="_blank"} version.

*Last update: `r Sys.Date()`*

------------------------------------------------------------------------
:::

## Current Position

```{r}
#| output: asis
#| echo: false
cv_events("current-position")
```

## Research

```{r}
#| output: asis
#| echo: false
cv_events("research")
```

## Education

```{r}
#| output: asis
#| echo: false
cv_events("education")
```

## Abroad

```{r}
#| output: asis
#| echo: false
cv_events("abroad")
```

## Publications

### Published

```{r}
#| output: asis
#| echo: false
cv_publications("Published")
```

### Under Review

```{r}
#| output: asis
#| echo: false
cv_publications("Under Review")
```

### Preregistration

```{r}
#| output: asis
#| echo: false
cv_publications("Preregistration")
```

### In Preparation

```{r}
#| output: asis
#| echo: false
cv_publications("In Preparation")
```

### Published Abstract

```{r}
#| output: asis
#| echo: false
cv_publications("Published Abstract")
```

## Conferences

```{r}
#| output: asis
#| echo: false
cv_conferences()
```

### Pre-conference workshops

```{r}
#| output: asis
#| echo: false
cv_bullets("preconf-workshops")
```

## Invited talks

```{r}
#| output: asis
#| echo: false
cv_bullets("invited-talks")
```

## Awards and Grants

```{r}
#| output: asis
#| echo: false
cv_bullets("awards")
```

## Peer Reviews

```{r}
#| output: asis
#| echo: false
cv_bullets("peer-reviews")
```

## Teaching

```{r}
#| output: asis
#| echo: false
cv_bullets("teaching")
```

## Academic Roles

```{r}
#| output: asis
#| echo: false
cv_bullets("academic-roles")
```

## Organizational Activities

```{r}
#| output: asis
#| echo: false
cv_bullets("organizational")
```

## Third Mission (Terza Missione)

```{r}
#| output: asis
#| echo: false
cv_events("third-mission")
```

## Research Groups Membership

```{r}
#| output: asis
#| echo: false
cv_events("research-groups")
```

## Collaborations

```{r}
#| output: asis
#| echo: false
cv_events("collaborations")
```

## Involvement in Research Groups

```{r}
#| output: asis
#| echo: false
cv_bullets("involvement")
```

## Training

```{r}
#| output: asis
#| echo: false
cv_events("training")
```

## Scientific Societies Membership

```{r}
#| output: asis
#| echo: false
cv_events("societies")
```

## Languages

```{r}
#| output: asis
#| echo: false
cv_events("languages")
```

## Programming Languages

```{r}
#| output: asis
#| echo: false
cv_events("programming")
```

## Research and Project Management Skills

```{r}
#| output: asis
#| echo: false
cv_events("skills")
```

## R Packages

```{r}
#| output: asis
#| echo: false
cv_bullets("r-packages")
```

## Operating Systems

```{r}
#| output: asis
#| echo: false
cv_events("systems")
```

------------------------------------------------------------------------

::: {.content-visible when-format="pdf"}
\footnotesize

I authorize the processing of personal data included in my CV in accordance with Legislative
Decree 101/2018 and the GDPR (Regulation EU 2016/679).
I hereby declare that the information and details provided in this Curriculum Vitae are true
and accurate to the best of my knowledge, acknowledging the legal and criminal consequences
of providing false statements as per Article 76 of Presidential Decree 445/2000.

\begin{center}
\textit{Last update: `r Sys.Date()`}
\end{center}
:::
